Critical Temperature of YBCO and BSCCO Superconductors

### 2014-12-04 Draft.tex
additional comments

Superconductors are materials that lose their electrical resistance  when they fall below a certain temperature. This is called the critical temperature. We determine the critical temperatures of two superconductors,  $\textrm{Yt}\textrm{Ba}_{2}\textrm{Cu}_{3}\textrm{O}_{7-\delta}$ and $\textrm{Bi}_{2}\textrm{Sr}_{2}\textrm{Ca}_{\textrm{n}-1}\textrm{Cu}_{\textrm{n}}\textrm{O}_{9}$ \textcolor{magenta}{to be}$xx \pm yy K$ \textcolor{magenta}{and} $uu \pm vv K$\textcolor{magenta}{respectively}, by measuring the voltage across the resistor as a function of temperature. \textcolor{red}{This reads as if you just measured the voltage, without passing any current. That would be a measurement of thermoelectric voltage, as with a thermocouple. You actually determined the critical temperature by passing a known current through the sample, measured the resulting voltage drop across the sample to find the resistance, then looked to see when the resistance became zero. }

>>>>

Superconductors are materials that lose their electrical resistance  when they fall below a certain temperature. This is called the critical temperature. We determine the critical temperatures of two superconductors,  $\textrm{Yt}\textrm{Ba}_{2}\textrm{Cu}_{3}\textrm{O}_{7-\delta}$ and $\textrm{Bi}_{2}\textrm{Sr}_{2}\textrm{Ca}_{\textrm{n}-1}\textrm{Cu}_{\textrm{n}}\textrm{O}_{9}$ \textcolor{magenta}{to be }$xx \pm yy \textrm{ K}$ \textcolor{magenta}{and } $uu \pm vv \textrm{ K}$\textcolor{magenta}{ respectively}, by measuring the voltage across the resistor as a function of temperature. \textcolor{red}{This reads as if you just measured the voltage, without passing any current. That would be a measurement of thermoelectric voltage, as with a thermocouple. You actually determined the critical temperature by passing a known current through the sample, measured the resulting voltage drop across the sample to find the resistance, then looked to see when the resistance became zero. Or reached the halfway point in the transition to zero. or some other criteria. }
